### 2014-09-11 paper/paper.Rmd
fixed gender reading code, next job to work on country and categorical variable labels so that they fit into the facet label windows better

```{r gendermaps2, fig.width=12, fig.height=7, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
#ggsave("gendermathmap.pdf", width=12, height=7)
ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey90")) + 
  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=rsig)) +
  scale_fill_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
  new_theme_empty + theme(legend.position="none")
#ggsave("genderreadmap.pdf", width=12, height=7)
#ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey90")) + 
#  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=ssig)) +
#  scale_fill_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
#  new_theme_empty + theme(legend.position="none")
```

>>>>

```{r gendermaps2, fig.width=12, fig.height=7, warning=FALSE, message=FALSE, echo=FALSE, cache=FALSE}
#ggsave("gendermathmap.pdf", width=12, height=7)
student2012.sub.summary.gap$name <- as.character(student2012.sub.summary.gap$name)
student2012.sub.map <- left_join(student2012.sub.summary.gap, world.polys)
student2012.sub.map$rsig <- factor(student2012.sub.map$rsig)
ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey90")) + 
  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=rsig)) +
  scale_fill_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
  new_theme_empty + theme(legend.position="none")
#ggsave("genderreadmap.pdf", width=12, height=7)
#ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey90")) + 
#  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=ssig)) +
#  scale_fill_manual("Significant", values=c("male"="skyblue", "female"="pink", "none"="lightgreen")) +
#  new_theme_empty + theme(legend.position="none")
```
